%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Hogan} \headerlastnamestyle{McDonald} \\
	\vspace{2mm}
	{\faEnvelope\ me@hoganmcdonald.com} | {\faMobile\ (651) 230 - 1107} | {\faMapMarker\ Minneapolis, MN} | {\faLink\ hoganmcdonald.com}
\end{center}
\cvsection{Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Languages:  & {\skill{ JavaScript, Python, Java, SQL}} \\
		Frameworks:  & {\skill{ React, AngularJs, React Native, Node.js, Express, PostgreSQL, MongoDB, TensorFlow, Keras, Numpy}} \\
		Tools:  & {\skill{ Git + Github, IntelliJ, PyCharm, Postman, GitLab}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

\vspace{-7mm}
\cvsection{Projects}
\begin{cventries}
	\cventry
	{Custom store locator using Google Maps JavaScript API, svg animation, and web design built on top of existing shopify theme.}
	{Odin \& Osgar}
	{Shopify, Liquid, Sass, Gulp, ThemeKit}
	{odinandosgar.com}
	{}
	
	\vspace{-5mm}
	\cventry
	{Custom messaging rest API for IoT devices. Sends custom text to voice messages when a device is triggered.}
	{Praeco - Lab651}
	{Twilio, Passport.js, Node.js, Express, Particle.io, AngularJs}
	{lab651.com/products}
	{}
	
	\vspace{-5mm}
	\cventry
	{Placed 2nd at 2017 Twin Cities Startup Week: Hack for Change. Uses custom machine learning algorithm and Nexosis API to predict a users date of death based on CDC historical data on mortality.}
	{I Know When You’re Going to Die - TCSW: Hack For Change}
	{Node.js, Express, Nexosis, Kaggle}
	{Iknowwhenyouregoingtodie.herokuapp.com}
	{}
	
	\vspace{-5mm}
	\cventry
	{Full stack web application that allows users to catalog ideas for blogs, speeches, and presentations. Uses IBM Watson API to provide sentiment analysis on user input..}
	{Capture - Prime Digital Academy}
	{AngularJs, PostgreSQL, Express, Node.js, Watson Cloud, Charts.js}
	{}
	{}
	
	\vspace{-5mm}
\end{cventries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Web Development Teaching Assistant}
	{Trilogy Education Services - University of Minnesota}
	{Minneapolis, MN}
	{Jan 2018 – Present}
	{\begin{cvitems}
		\item {Graded all student assignments and provided timely feedback on best practices.}
		\item {O ff ered one on one support to students with diverse backgrounds.}
		\item {Collaborated with other staff on shaping Web Development curriculum to meet the needs of local job market.}
		\end{cvitems}}
	\cventry
	{Store Lead}
	{Words Bookstore}
	{MSP Airport}
	{Sep 2016 – Aug 2017}
	{\begin{cvitems}
		\item {Trained employees on visual and opperational standards for the store.}
		\item {Designed merchandise that accounted for 20\% of sales.}
		\end{cvitems}}
	\cventry
	{Community Engagement Coordinator}
	{Bloom Church}
	{St. Paul, MN}
	{May 2015 – Mar 2016}
	{\begin{cvitems}
		\item {Developed systems for communication between staff and volunteers.}
		\item {Wrote and delivered sermons at least monthly.}
		\item {Mentored community voluneteers on strategies for leading small group curriculums.}
		\end{cvitems}}
\end{cventries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{Full Stack Software Engineering Certification}
	{Prime Digital Academy}
	{Minneapolis, MN}
	{Aug 2017}
	{}
	\cventry
	{Pastoral Theology - Generals}
	{North Central University}
	{Minneapolis, MN}
	{Sep 2013 – Sep 2015}
	{}
\end{cventries}

\vspace{-2mm}

\ 
\end{document}